---
title: "marineSim: a tutorial"
author: "Ebenezer Afrifa-Yamoah"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
output:
  rmarkdown::html_vignette:
    toc: true
    toc_depth: 2
vignette: >
  %\VignetteIndexEntry{marineSim: a tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", fig.width = 7, fig.height = 4.2,
                      fig.align = "center", dpi = 96)
options(width = 100)
```

## 1. Scope

`marineSim` is the simulation engine behind the article *Spatio-temporal random
forests with adaptive local features for marine species distribution modelling
under data limitation* (Afrifa-Yamoah, Fouedjio, Mueller, McMahon and Hyndes,
submitted to *Methods in Ecology and Evolution*). The package generates synthetic
marine ecosystems, draws survey data from them under three sampling designs,
engineers the four feature blocks of the spatio-temporal random forest (stRF),
fits and scores the competing models, and attributes the predictive gain of stRF
to its components by an exact Shapley decomposition with a cluster bootstrap.

This tutorial walks through that pipeline on a small scale. It is written so that
every code chunk runs in a few seconds to a couple of minutes on one core, and so
that each object can be inspected along the way. The full benchmark of the
article (3,779 datasets) is driven by the scripts in the repository's
`analysis/` directory; Section 10 explains how the pieces shown here map onto
those scripts and how a single archived result can be recomputed exactly.

Section numbers in the text refer to the article. Numerical values printed in
this document come from the small examples below and are not the article's
estimates; the comparison between the two is discussed where relevant.

```{r load}
library(marineSim)
```

## 2. Installation

The package depends only on R (4.1 or later) and `ranger`. From the repository
root:

```r
install.packages("ranger")
install.packages("marineSim", repos = NULL, type = "source")
```

or directly from GitHub, where the package lives in the `marineSim/` subdirectory:

```r
remotes::install_github("EAfrifa-Yamoah/marineSim", subdir = "marineSim")
```

Forest fits are seeded and single threaded (`num.threads = 1`), so a given seed
gives the same score on the same `ranger` version. A different `ranger` version
may change the forest's random stream and therefore the third or fourth decimal
of a score; the mechanisms and orderings shown here do not depend on it.

## 3. The simulated ecosystem

### 3.1 Fixed design constants

The engine works on a square grid of `GRID` by `GRID` cells covering
`EXTENT_KM` kilometres a side. The constants are exported so that scripts can
refer to them by name. They are part of the design: changing any of them changes
the random stream and with it every reported number.

```{r constants}
c(GRID = GRID, EXTENT_KM = EXTENT_KM, CELL_KM = CELL_KM, N_TEST = N_TEST,
  RF_TREES = RF_TREES, N_ANCHORS = N_ANCHORS)
RADII_KM
BLOCKS
```

### 3.2 Generating a world

`make_world()` builds one ground truth ecosystem (Section 3.1). Four standardised
Matérn covariate fields are simulated by spectral synthesis: depth, substrate and
wave exposure are static, and sea surface temperature (SST) follows an AR(1)
process in time. A latent spatial field at the world's correlation range, a
persistent site effect and a habitat mask of structural zeros complete the
linear predictor. Occurrence is Bernoulli and abundance is Poisson, both
multiplied by the mask.

The two arguments that define a world configuration in the article are
`stationary` (whether the depth and SST coefficients vary in space) and
`range_km` (the correlation range of the latent field: 30, 80 or 200 km).

```{r world}
w <- make_world(stationary = FALSE, range_km = 80, n_time = 5, seed = 11)
str(w, max.level = 1, give.attr = FALSE)
```

Static fields are `GRID` by `GRID` matrices; quantities that change through time
(`sst`, `eta`, `p`, `y`, `mu`, `ycount`) are lists with one matrix per timestep.
The helper below draws a field with cell centres on the kilometre axes. The
matrix is transposed because `image()` expects its first index to run along `x`,
whereas the engine stores rows along `y`.

```{r show-field, fig.width = 9, fig.height = 3.4}
axis_km <- seq(CELL_KM / 2, EXTENT_KM - CELL_KM / 2, by = CELL_KM)
show_field <- function(m, main, col = hcl.colors(24, "viridis")) {
  image(axis_km, axis_km, t(m), col = col, main = main, xlab = "x (km)", ylab = "y (km)",
        useRaster = TRUE)
}
op <- par(mfrow = c(1, 3), mar = c(4, 4, 2.5, 1), pty = "s")
show_field(w$depth, "Depth (standardised)")
show_field(w$eta[[5]], "Linear predictor, t = 5")
show_field(w$p[[5]], "Occurrence probability, t = 5")
par(op)
```

The habitat mask is visible as the flat zero region of the probability surface.
Its extent is one quarter of the domain by construction:

```{r mask}
mean(w$mu[[1]] == 0)
```

Only SST changes through time, so the difference between the linear predictor at
two timesteps equals the SST coefficient field times the SST change. This
identity is one of the mechanism checks in the package's test suite.

```{r sst-identity}
resid <- (w$eta[[5]] - w$eta[[1]]) - w$b_sst * (w$sst[[5]] - w$sst[[1]])
max(abs(resid))
```

### 3.3 Cell indexing and covariates

Cells are indexed from 1 to `GRID^2` in column major order. `cell_xy()` returns
the centre of each cell in kilometres and `covariates()` reads the four
covariates at a set of cells and a timestep.

```{r cells}
idx <- c(1, 50, 51, 2500)
cbind(idx, cell_xy(idx))
head(covariates(w, idx, t = 5), 2)
```

### 3.4 The article's six configurations

`world_grid()` enumerates the two stationarity regimes crossed with the three
latent ranges, and derives a seed for every field realisation. The benchmark uses
realisations 0 to 5, giving 36 independent worlds. The first configuration of
realisation 0 is shown below.

```{r world-grid}
grid <- world_grid(realisations = 0:1)
length(grid)
str(grid[[1]])
sapply(grid, function(g) g$cfg)
```

## 4. Survey designs

`sample_sites()` draws `n` distinct cells under one of three designs (Section
3.2). Random sampling is simple random sampling of cells. Clustered sampling
places three Gaussian clusters whose centres are uniform on the central 70
percent of each axis. Stratified sampling partitions the grid into equal blocks
and draws one cell in each of `n` blocks chosen without replacement.

```{r designs, fig.width = 9, fig.height = 3.4}
set.seed(3)
designs <- c("random", "clustered", "stratified")
sites <- lapply(designs, function(d) cell_xy(sample_sites(100, d)))
op <- par(mfrow = c(1, 3), mar = c(4, 4, 2.5, 1), pty = "s")
for (k in 1:3) {
  show_field(w$p[[5]], paste0(designs[k], " (n = 100)"), col = hcl.colors(24, "Grays", rev = TRUE))
  points(sites[[k]], pch = 21, bg = "#D55E00", cex = 0.9)
}
par(op)
```

The clustered design is the data limited regime of most interest in the article:
it leaves large parts of the domain unobserved, which is where spatial features
built from the training sites can either help or extrapolate badly.

## 5. From a world to a benchmark dataset

### 5.1 Building a dataset

`build_dataset()` draws the sites, observes the response at every timestep,
holds out `N_TEST` cells that are not sites, and constructs the four feature
blocks at the final timestep for both the training sites and the test cells
(Sections 3.2 and 3.3).

```{r dataset}
ds <- build_dataset(w, n = 100, n_time = 5, design = "clustered", seed = 7)
names(ds)
c(train = length(ds$y_tr), test = length(ds$y_te), positives_train = sum(ds$y_tr))
sapply(ds$btr, ncol)
```

The blocks are stored as two parallel lists, `btr` for the training sites and
`bte` for the test cells, with one matrix per block:

| Block | Columns | Content |
|---|---|---|
| `COORD` | 2 | cell centre coordinates in km |
| `EDF` | up to `N_ANCHORS` | distance to k-means anchors of the training sites |
| `LAG` | `length(RADII_KM)` | mean training response within 25, 75 and 150 km |
| `TEMP` | 2 | previous timestep response and site history mean, read at the nearest training site |
| `NN0` | 1 | same timestep response of the nearest training site (a control, not part of stRF) |

Every block is a function of the training sites and the training responses
only. The test responses `y_te` are never an argument to any block builder.
Perturbing a training response moves the test lag features, which shows that the
guard is not vacuous:

```{r leakage}
lag_a <- spatial_lags(ds$btr$COORD, ds$y_tr, ds$bte$COORD, is_train = FALSE)
y_pert <- ds$y_tr; y_pert[1] <- 1 - y_pert[1]
lag_b <- spatial_lags(ds$btr$COORD, y_pert, ds$bte$COORD, is_train = FALSE)
sum(lag_a != lag_b)
"y_te" %in% c(names(formals(spatial_lags)), names(formals(nearest_train)), names(formals(edf)))
```

At the training sites the spatial lags are computed leave one out, so a site's
own response never enters its lag features:

```{r lag-loo}
lags <- ds$btr$LAG; colnames(lags) <- paste0("lag_", RADII_KM, "km")
head(cbind(y = ds$y_tr, lags), 4)
```

### 5.2 The temporal placebo

With a single timestep there is no history to read, and the temporal block is
filled with the training mean at every row. This is the placebo condition of the
article: a block that carries no information must receive a Shapley value close
to zero, and any non zero attribution to it measures the noise floor of the
decomposition.

```{r placebo}
ds1 <- build_dataset(w, n = 100, n_time = 1, design = "clustered", seed = 7)
unique(as.vector(ds1$btr$TEMP))
```

### 5.3 Imperfect detection and abundance

Two extensions of the benchmark are switches on the same function. A detection
probability below one thins the positives at the training sites only; the test
truth is untouched. The abundance response replaces occurrence with Poisson
counts.

```{r extensions}
ds_thin <- build_dataset(w, 100, 5, "clustered", seed = 7, detection = 0.7)
c(full = sum(ds$y_tr), thinned = sum(ds_thin$y_tr), same_sites = identical(ds_thin$site, ds$site))
ds_cnt <- build_dataset(w, 100, 5, "clustered", seed = 7, response = "abundance")
summary(ds_cnt$y_tr)
```

`build_dataset()` returns `NULL` when the training or test response is
degenerate (all zeros or all ones), which can happen at the smallest sample
sizes. The benchmark runner skips such datasets.

## 6. Fitting and scoring

`score()` fits the forest backbone of the article on the four covariates plus a
coalition of blocks and returns a single held out score: the AUC for occurrence,
or the Spearman correlation with the held out counts for abundance. `glm_score()`
fits the covariate only GLM baseline. Three coalitions have names in the article:

| Coalition | Model |
|---|---|
| `character(0)` | standard random forest on covariates |
| `"COORD"` | spatial random forest |
| `BLOCKS` | stRF |

```{r scores}
c(GLM = glm_score(ds),
  RF = score(ds, character(0), seed = 7),
  spatial_RF = score(ds, "COORD", seed = 7),
  stRF = score(ds, BLOCKS, seed = 7))
```

On this dataset the covariate only forest scores below the GLM. The algorithmic
term of the decomposition is exactly that difference, and at small sample sizes
it is often negative for a single dataset; only its average over many datasets
is interpretable.

The forest is a probability forest with `RF_TREES` trees, minimum node size 1
and `mtry = floor(sqrt(p))`. For abundance the response is `log1p(count)` and
`mtry = p`. The AUC is computed by the rank statistic:

```{r auc}
auc(c(0, 0, 1, 1), c(0.1, 0.4, 0.35, 0.8))
```

## 7. Coalitions and the exact Shapley decomposition

The attribution of Section 3.4 asks how much of the gain of stRF over the
covariate only forest is due to each block. Because blocks interact (distance
fields and coordinates both encode location), the answer is not the sum of
single block gains. The article uses the exact Shapley value over the 16
coalitions of `BLOCKS`, which requires fitting every coalition.

`required_subsets()` lists the 16 coalitions plus four control coalitions that
include `NN0`; `skey()` gives the column name under which each score is stored.

```{r subsets}
subs <- required_subsets()
length(subs)
sapply(subs, skey)
```

Fitting all twenty on one dataset takes a few seconds:

```{r one-row}
row <- as.list(sapply(subs, function(S) score(ds, S, seed = 7)))
names(row) <- sapply(subs, skey)
phi <- shapley_row(row)
round(phi, 4)
```

The Shapley values satisfy the efficiency property: they sum to the gain of the
full coalition over the empty one. This holds exactly, which is a useful check
whenever the decomposition code is modified.

```{r efficiency}
c(sum_phi = sum(phi), full_minus_base = row[[skey(BLOCKS)]] - row[[skey(character(0))]])
```

On this one clustered dataset the distance field block receives the largest
share. A single dataset is, however, a single draw of sites and of forest
randomness. The article's claims rest on averages over many datasets and on
intervals that respect the dependence between datasets drawn from the same
world.

## 8. A small benchmark with the cluster bootstrap

The chunk below is a reduced version of `analysis/01_ablation_expanded.R`. It
takes two world configurations (stationary and non stationary at 80 km), three
field realisations of each, two designs and two timestep spans, at a single
sample size. Each dataset yields one row with the GLM score and the twenty
coalition scores, in exactly the format the runner writes to
`results/ablation_expanded.csv`. The seed of every dataset is a deterministic
function of its description through `dataset_seed()`, so a row can be recomputed
in isolation.

```{r small-benchmark, cache = FALSE}
run_small_benchmark <- function(cfgs, realisations, designs, n, timesteps) {
  grid <- Filter(function(g) g$cfg %in% cfgs, world_grid(realisations))
  out <- list()
  for (wg in grid) {
    w <- make_world(wg$stat, wg$range_km, n_time = max(timesteps), seed = wg$seed)
    for (di in seq_along(designs)) for (nt in timesteps) {
      dseed <- dataset_seed(wg$seed, n, nt, di)
      d <- build_dataset(w, n, nt, designs[di], dseed)
      if (is.null(d)) next
      rec <- data.frame(design = designs[di], world_cfg = wg$cfg, realisation = wg$real,
                        n = n, n_time = nt, GLM = glm_score(d), stringsAsFactors = FALSE)
      for (S in subs) rec[[skey(S)]] <- score(d, S, seed = dseed %% 10000L)
      out[[length(out) + 1]] <- rec
    }
  }
  do.call(rbind, out)
}
t0 <- Sys.time()
bench <- run_small_benchmark(cfgs = c("stat_r80", "nonstat_r80"), realisations = 0:2,
                             designs = c("random", "clustered"), n = 100, timesteps = c(1, 5))
c(datasets = nrow(bench), columns = ncol(bench),
  minutes = round(as.numeric(difftime(Sys.time(), t0, units = "mins")), 1))
```

`add_shapley()` appends the Shapley values and the derived quantities used in
the tables of the article: the algorithmic term (covariate only forest minus
GLM), the total gain over the GLM, the temporal increment when added last, the
same increment with the `NN0` control present, and the spatial total. It also
adds a `field` identifier that combines the configuration and the realisation;
this is the bootstrap cluster.

```{r add-shapley}
bench <- add_shapley(bench)
head(bench[, c("design", "n_time", "field", "GLM", "alg", "phi_COORD", "phi_EDF", "phi_LAG", "phi_TEMP", "total")], 4)
table(bench$field)
```

### 8.1 Why the bootstrap resamples fields rather than datasets

Datasets drawn from the same world share its covariate fields, latent structure
and habitat mask, so they are not independent. Treating them as such would make
intervals too narrow. `boot_ci()` resamples the independent field realisations
with replacement and takes the mean of the field means in each replicate. The
point estimate remains the dataset level mean.

```{r boot}
boot_ci(bench[bench$n_time == 5, ], "phi_EDF")
```

`decomp_table()` produces one row per component for a subset of datasets, with
the interval and the share of the total gain:

```{r decomp}
A <- bench[bench$n_time == 5, ]
tab <- rbind(decomp_table(A, "pooled"),
             decomp_table(A[A$design == "random", ], "random"),
             decomp_table(A[A$design == "clustered", ], "clustered"))
tab$value <- round(tab$value, 3); tab$ci_lo <- round(tab$ci_lo, 3)
tab$ci_hi <- round(tab$ci_hi, 3); tab$share_pct <- round(tab$share_pct, 1)
tab[, c("subset", "component", "value", "ci_lo", "ci_hi", "share_pct", "n_datasets", "n_fields")]
```

```{r decomp-plot, fig.height = 3.8}
comp <- c("Algorithmic flexibility", "Coordinates", "Distance fields", "Spatial lags", "Temporal")
m <- sapply(c("random", "clustered"), function(s)
  tab$value[tab$subset == s][match(comp, tab$component[tab$subset == s])])
rownames(m) <- comp
op <- par(mar = c(4, 9, 2, 1))
barplot(t(m), beside = TRUE, horiz = TRUE, las = 1, col = c("#0072B2", "#D55E00"),
        xlab = "Contribution to AUC gain over the GLM (T = 5, n = 100)", legend.text = TRUE,
        args.legend = list(x = "bottomright", bty = "n"))
abline(v = 0, lty = 3)
par(op)
```

### 8.2 The temporal placebo and the NN0 control

The same table can be computed by timestep span. At `n_time = 1` the temporal
block is constant, so its Shapley value estimates the noise floor of the
decomposition. The two "added last" quantities ask a different question: how
much does the temporal block add once all spatial blocks are present, and does
that increment survive when the same timestep nearest neighbour response
(`NN0`) is also available? The second one separates genuine temporal information
from information that a spatial neighbour would have supplied anyway.

```{r temporal}
do.call(rbind, lapply(c(1, 5), function(T) {
  s <- bench[bench$n_time == T, ]
  data.frame(n_time = T,
             shapley_TEMP = round(boot_ci(s, "phi_TEMP")[["value"]], 4),
             added_last = round(boot_ci(s, "temp_added_last")[["value"]], 4),
             added_last_NN0 = round(boot_ci(s, "temp_marg_withNN0")[["value"]], 4),
             n_datasets = nrow(s))
}))
```

### 8.3 Reading these numbers

The benchmark above has six fields and twelve datasets per timestep span. Its
intervals are wide, and the values are specific to one sample size and two
configurations. They illustrate the machinery rather than estimate the article's
quantities, which rest on 36 fields, five sample sizes, three designs and four
timestep spans. What should carry over, and is worth checking against your own
run, is the structure: a placebo value near zero at `n_time = 1`, a spatial total
that dominates the gain, and a smaller contribution of the clustered design's
spatial lags, which have fewer neighbours to average.

## 9. Area of applicability

Spatial features built from the training sites are only as good as the coverage
of those sites. `area_of_applicability()` implements the dissimilarity index of
Meyer and Pebesma (2021, *Methods in Ecology and Evolution* 12, 1620 to 1633):
the distance of each query point to its nearest training point in standardised
predictor space, relative to the typical nearest neighbour distance within the
training set. Points whose index exceeds the 95th percentile of the within
training indices are flagged as outside the area of applicability.

The predictor space used below is the four covariates plus the coordinates,
which is the space in which a spatial random forest partitions the domain. The
function also accepts an `importance` vector so that predictors can be weighted
by their contribution to the fitted model, as in Supplement S9.

```{r aoa}
train_pred <- cbind(ds$Xc_tr, ds$btr$COORD)
query_pred <- cbind(ds$Xc_te, ds$bte$COORD)
a <- area_of_applicability(train_pred, query_pred)
c(threshold = round(a$threshold, 3), share_inside = round(mean(a$inside), 3))
```

```{r aoa-map, fig.width = 5.6, fig.height = 5.6}
op <- par(mar = c(4, 4, 2.5, 1), pty = "s")
show_field(w$p[[5]], "Area of applicability, clustered design",
           col = hcl.colors(24, "Grays", rev = TRUE))
points(ds$bte$COORD, pch = 15, cex = 0.55, col = ifelse(a$inside, "#0072B2", "#D55E00"))
points(ds$btr$COORD, pch = 21, bg = "white", cex = 0.9)
legend("topleft", legend = c("site", "test cell inside", "test cell outside"), pch = c(21, 15, 15),
       pt.bg = "white", col = c("black", "#0072B2", "#D55E00"), bg = "white", cex = 0.85)
par(op)
```

Two kinds of cell fall outside the area of applicability: cells far from the
three clusters, whose coordinates are unlike any site's, and cells whose
covariate combination was never observed at a site, which in this world
coincide with the darker high probability patches. Predictions there rely on
extrapolating the covariate response and on lag features that fall back to the
training mean, which is one reason the clustered design is the hardest regime
in the benchmark.

## 10. Reproducing the article

### 10.1 The verification protocol

The repository ships the mechanism checks of Sections 3.1 to 3.3 both as the
package's `testthat` suite and as a human readable script. Run the script first
on any new machine; every line must read `PASS`.

```bash
cd analysis
Rscript 00_verify_engine.R
```

### 10.2 The benchmark stages

`analysis/01_ablation_expanded.R` runs four stages with the function shown in
Section 8, extended to five sample sizes and the full set of realisations:

| Stage | Response | Detection | Designs | Realisations | Timesteps |
|---|---|---|---|---|---|
| A_designs | occurrence | 1.0 | all three | 0 to 5 | 1, 3, 5 |
| B_T10 | occurrence | 1.0 | all three | 0 to 5 | 10 |
| C_detect | occurrence | 0.7 | all three | 0 to 2 | 1, 3, 5 |
| D_abundance | abundance | 1.0 | all three | 0 to 2 | 1, 3, 5 |

The runner is resumable and shardable because every dataset is identified by
its key (response, detection, design, configuration, realisation, `n`, `n_time`,
replicate) and seeded by `dataset_seed()` from that key. Completed keys are
skipped on restart, and shards running on different cores produce identical
rows. `02_decompose.R` then applies `add_shapley()` and `decomp_table()` to the
merged table to produce the decomposition tables of the article.

### 10.3 Recomputing one archived row

The seeding scheme means that any row of `results/ablation_expanded.csv` can be
recomputed from its key alone. The chunk below is not evaluated when the
vignette is built, since the archive lives outside the package; run it from the
repository root with the package installed. Note that stage A worlds are built
with five timesteps, the maximum of that stage, whatever the `n_time` of the row,
because the world's random stream must be identical across all datasets drawn
from it.

```{r recompute, eval = FALSE}
d <- read.csv("results/ablation_expanded.csv", check.names = FALSE, stringsAsFactors = FALSE)
r <- d[d$stage == "A_designs" & d$design == "clustered" & d$world_cfg == "nonstat_r80" &
       d$realisation == 1 & d$n == 100 & d$n_time == 5, ][1, ]
wg <- Filter(function(g) g$cfg == r$world_cfg && g$real == r$realisation, world_grid(r$realisation))[[1]]
w_r <- make_world(wg$stat, wg$range_km, n_time = 5, seed = wg$seed)
di <- match(r$design, c("random", "clustered", "stratified"))
dseed <- dataset_seed(wg$seed, r$n, r$n_time, di, r$rep, r$detection, r$response)
d_r <- build_dataset(w_r, r$n, r$n_time, r$design, dseed, r$detection, r$response)
mine <- c(GLM = glm_score(d_r), sapply(required_subsets(), function(S) score(d_r, S, dseed %% 10000L)))
names(mine) <- c("GLM", sapply(required_subsets(), skey))
max(abs(mine - unlist(r[names(mine)])))
```

On the machine used to prepare this tutorial (R 4.3.3, ranger 0.16.0, x86_64
Linux) the maximum absolute difference across the 21 score columns was below
`1e-15`. A difference at the third decimal or beyond on your machine most likely
indicates a different `ranger` version rather than an error in the key.

### 10.4 Figures and the case study

The figure scripts in `figures/scripts/` read only `results/` and draw every
figure of the article and its Supplement with `ggplot2`. The *Posidonia sinuosa*
case study (`analysis/08_case_study.R`) applies the same four blocks to
monitoring data from five Western Australian marine parks; those data are not
redistributed, so that script requires the file described under *Data
availability* in the README.

## 11. Extending the engine

The pieces of the pipeline are deliberately separable.

**A new feature block.** `score()` binds the covariates to whichever matrices in
`ds$btr` and `ds$bte` are named in its `subset` argument. A new block is
therefore a pair of matrices added to those two lists, with the same number of
rows as the training sites and the test cells respectively. To include it in the
Shapley decomposition, extend `BLOCKS` in a fork of the package, because
`required_subsets()` and `shapley_row()` enumerate coalitions from that
constant; the number of coalitions doubles with each added block.

**A new sampling design.** Any function that returns `n` distinct cell indices
in `1:GRID^2` can replace `sample_sites()` inside a copy of `build_dataset()`.
The leave one out convention for the lags and the exclusion of sites from the
test pool are handled downstream and need no change.

**A different scoring rule.** `score()` returns one number per fit. A
replacement that returns, for example, the log loss or a calibration measure
feeds `shapley_row()` unchanged, since the decomposition is defined on whatever
value function the coalitions are scored with.

**Changing the constants.** The grid size, the number of test cells, the forest
size, the anchor count and the lag radii are fixed at package level. They are
not function arguments because the article's seeds and archived results depend
on them. A sensitivity analysis over these choices belongs in a fork with its
own seeds, not in a parameter sweep on the installed package.

## 12. Session information

```{r session}
sessionInfo()
```
